Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2023-12-20 Manuscript Analyses/manuscript_analysis.Rmd
Reformatted analysis rmd file
participant demo and cog des stats

@@

@@

>>>>

## Participant Demographics

@@

demo <- rio::import("participant_demo.csv")

@@

cog <- rio::import("cleaned_data.csv") %>%
  dplyr::select(c(id, speaker, list_sort_c:win_l)) %>%
  dplyr::mutate(best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
  dplyr::distinct()

age <- demo %>%
  select(id, age)

cog_scores <- left_join(age, cog, by = "id")

cog_scores %>%
  dplyr::group_by(speaker) %>%
  furniture::table1(age, list_sort_c, flanker_c, card_sort_c, vocab_c, pattern_c, 
                    pic_seq_c, fluid_cog_c, best_win,
                    test = T, 
                    export = "cog_score")
